---
title: "Untitled"
output: pdf_document
header-includes:
  - \usepackage{tipa}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("academicWriteR")
library("lme4")
library("lmerTest")
library("brms")
library("tidyverse")
```

```{r, test, eval=T}
# Testing: try to see if you can determine the doc type and use it to 
# set how the functions work
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
use_latex <- dplyr::if_else(doc_type == "latex", TRUE, FALSE)
doc_type
use_latex
```


## Fit models and inline printing

```{r, fit-model, echo=TRUE, cache=TRUE, warning=F, message=F, results='hide'}
mod1 <- lm(mpg ~ wt * drat, data = mtcars)
mod2 <- glm(mpg ~ wt, data = mtcars, family = "gaussian")
mod3 <- lmer(Reaction ~ 1 + Days + (1|Subject), data = sleepstudy)
mod4 <- glmer(cbind(incidence, size - incidence) ~ period + (1 | herd),
              data = cbpp, family = binomial)
mod5 <- brm(mpg ~ wt, data = mtcars, file = here::here("testing_files", "mod5"))
```


`r print_model_param(mod1, "wt")`  
`r print_model_param(mod2, "(Intercept)")`  
`r print_model_param(mod3, "(Intercept)")`  
`r print_model_param(mod4, "(Intercept)")`  
`r print_model_param(mod5, "wt")`



\clearpage

```{=openxml}
<w:p>
  <w:r>
    <w:br w:type="page"/>
  </w:r>
</w:p>
```




# Printing models to tables

## lm

```{r, tester-word-lm, eval=T}
mod_to_table(
  mod1, 
  font_size = 12, 
  left_align = 1, 
  param_names = c(Intercept = "(Intercept)", 
                  WT = "wt", 
                  DRAT = "drat", 
                  `WT x DRAT` = "wt:drat"), 
  col = c(1, 2), width = 1.5
  )

```

<br>

## lmer

```{r, tester-word-lmer, eval=T}
mod_to_table(
  mod3, 
  font_size = 12, 
  left_align = 1, 
  param_names = c(Intercept = "(Intercept)"), 
  col = 1, width = 1.5
  )

```

<br>


## glmer

```{r, tester-word-glmer, eval=T}
mod_to_table(
  mod4, 
  font_size = 12, 
  left_align = 1, 
  param_names = c(Intercept = "(Intercept)"), 
  col = 1, width = 1.5
  )
```

<br>

## brms

```{r, tester-word-brms, eval=T, warning=T}
mod_to_table(
  mod5, 
  font_size = 12, 
  left_align = 1, 
  #param_names = c(Intercept = "b_Intercept"), 
  col = c(1, 3), width = 1.5
  )
```



```{=openxml}
<w:p>
  <w:r>
    <w:br w:type="page"/>
  </w:r>
</w:p>
```








```{r, func-test, eval=F}
mod_to_table(
  mod1, font_size = 11, 
  param_names = c(Intercept = "(Intercept)", 
                  `$\\delta VOT_{hi}$` = "wt", 
                  `\\textipa{[BSsoODP]}` = "drat"))
```


- TO address
  - captions
  - use actual minus sign for negative numbers
  - html functionality for mod_to_table
  - add unit tests
  - prob beta not equal to 0





