---
title: "Untitled"
output: pdf_document
header-includes:
  - \usepackage{tipa}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(academicWriteR)
library(lme4)
library(lmerTest)
library(brms)
```

```{r, test, eval=F, echo=T}
# Testing: try to see if you can determine the doc type and use it to 
# set how the functions work
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
use_latex <- ifelse(doc_type == "latex", yes = TRUE, no = FALSE)
doc_type
use_latex
```




```{r, fit-model, echo=TRUE, cache=TRUE, warning=F, message=F, results='hide'}
mod1 <- lm(mpg ~ wt * drat, data = mtcars)
mod2 <- glm(mpg ~ wt, data = mtcars, family = "gaussian")
mod3 <- lmer(Reaction ~ 1 + Days + (1|Subject), data = sleepstudy)
mod4 <- glmer(cbind(incidence, size - incidence) ~ period + (1 | herd),
              data = cbpp, family = binomial)
mod5 <- brm(mpg ~ wt, data = mtcars)
```


`r print_model_param(mod1, "wt")`  
`r print_model_param(mod2, "(Intercept)")`  
`r print_model_param(mod3, "(Intercept)")`  
`r print_model_param(mod4, "(Intercept)")`  
`r print_model_param(mod5, "wt")`






# printing models to tables



```{r, tester-word-lm, eval=T}
mod_to_table(
  mod1, 
  font_size = 12, 
  left_align = 1, 
  param_names = c(Intercept = "(Intercept)", 
                  WT = "wt", 
                  DRAT = "drat", 
                  `WT x DRAT` = "wt:drat"), 
  col = c(1, 2), width = 1.5
  )

```

<br>

```{r, tester-word-lmer, eval=T}
mod_to_table(
  mod3, 
  font_size = 12, 
  left_align = 1, 
  param_names = c(Intercept = "(Intercept)"), 
  col = 1, width = 1.5
  )

```

<br>

```{r, tester-word-glmer, eval=T}
mod_to_table(
  mod4, 
  font_size = 12, 
  left_align = 1, 
  param_names = c(Intercept = "(Intercept)"), 
  col = 1, width = 1.5
  )
```

<br>

```{r, tester-word-brms, eval=T}
mod_to_table(
  mod5, 
  font_size = 12, 
  left_align = 1, 
  param_names = c(Intercept = "(Intercept)"), 
  col = 1, width = 1.5
  )
```







special chars (subscripts, superscripts, IPA, math)

```{r, built-kable-table, eval=F}
hold <- suppressWarnings(broom::tidy(mod3, conf.int = TRUE))

hold %>% 
  kable(., format = "latex", booktabs = T, escape = T, 
           caption = 'Posterior parameter estimates for voiced stops.', 
           align = "r") %>% 
  kable_styling(font_size = 11, latex_options = c("hold_position"))  

```




```{r, func-test}
mod_to_table(
  mod1, font_size = 11, 
  param_names = c(Intercept = "(Intercept)", 
                  `$\\delta VOT_{hi}$` = "wt", 
                  `\\textipa{[BSsoODP]}` = "drat"))
```


- TO address
  - captions
  - use actual minus sign for negative numbers
  - html functionality for mod_to_table
  - add unit tests
  - prob beta not equal to 0



`r count_words(file = "~/Desktop/Untitled.Rmd")`